COG-ED Manuscript

### 2022-01-07 06_Paper/COG-ED/Manuscript.Rmd
updated ref to Singmann

We aim to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100 ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
Aggregated RT values will be described using the median and the median of absolute deviation (MAD) as robust estimates of center and variability, respectively [@Lachaud2011].
Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in multi-level-model (MLM), because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2017]. 
Declining performance will be investigated by calculating an rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
For each ED round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
An rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Tukey method will be used for the paired contrasts of each rmANOVA, including *p*-value adjustment.

>>>>

We aim to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100 ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
Aggregated RT values will be described using the median and the median of absolute deviation (MAD) as robust estimates of center and variability, respectively [@Lachaud2011].
Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in multi-level-model (MLM), because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2019]. 
Declining performance will be investigated by calculating an rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
For each ED round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
An rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Tukey method will be used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
